A Horrocks-type theorem for even orthogonal $K_2$

### 2021-02-10 dl-paper.tex
Clearer sentence in lem:prop41

\begin{lemma} \label{lem:prop41}
Assume additionally that the residue field $k$ is of characteristic $\neq 2$.
Then the canonical homomorphism $f\colon C(\rD_\ell, B, I) \to C(\rD_\ell, R, I)$ is surjective for $\ell \geq 7$. \end{lemma}
\begin{proof}
Writing the starting portion of the homology long exact sequence for the homomorphism $\St(\rD_\ell, R) \to \St(\rD_\ell, R/I)$ 
and using the isomorphisms of~\cref{lem:relativeH3} and~\cref{lem:lowerKgroups} we obtain the following commutative diagram:
\[\begin{tikzcd} \KO_3(2\ell, B) \arrow{r} \arrow{d} & \KO_3(2\ell, k[X^{-1}]) \arrow{d}[swap]{f'} \ar[r, twoheadrightarrow] & \ar{d}[swap]{f} C(\rD_\ell, B, I) \\
 \KO_3(2\ell, R) \arrow{r} & \KO_3(2\ell, k[X, X^{-1}]) \ar[r, twoheadrightarrow] & C(\rD_\ell, R, I). \end{tikzcd} \]
By~\cref{Panin-stability} the homomorphism $f'$ can be identified with the canonical map $\GW_3^{[0]}(k[X^{-1}]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
By~\cref{bass-ft} $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k),$
but since the group $\GW_2^{[3]}(k)$ is trivial by~\cite[Lemma~2.2]{FRS12}, the homomorphism $f'$ (and hence $f$) is surjective.
\end{proof}

>>>>

\begin{lemma} \label{lem:prop41}
Assume additionally that the residue field $k$ is of characteristic $\neq 2$.
Then the canonical homomorphism $f\colon C(\rD_\ell, B, I) \to C(\rD_\ell, R, I)$ is surjective for $\ell \geq 7$. \end{lemma}
\begin{proof}
Writing down the starting portions of the homology long exact sequences for the homomorphisms $\St(\rD_\ell, R) \to \St(\rD_\ell, R/I)$, $\St(\rD_\ell, B) \to \St(\rD_\ell, B/I)$ and using the isomorphisms of~\cref{lem:relativeH3} and~\cref{lem:lowerKgroups} we obtain the following commutative diagram:
\[\begin{tikzcd} \KO_3(2\ell, B) \arrow{r} \arrow{d} & \KO_3(2\ell, k[X^{-1}]) \arrow{d}[swap]{f'} \ar[r, twoheadrightarrow] & \ar{d}[swap]{f} C(\rD_\ell, B, I) \\
 \KO_3(2\ell, R) \arrow{r} & \KO_3(2\ell, k[X, X^{-1}]) \ar[r, twoheadrightarrow] & C(\rD_\ell, R, I). \end{tikzcd} \]
By~\cref{Panin-stability} the homomorphism $f'$ can be identified with the canonical map $\GW_3^{[0]}(k[X^{-1}]) \to \GW_3^{[0]}(k[X, X^{-1}])$.
By~\cref{bass-ft} $\GW_3^{[0]}(k[X, X^{-1}]) \cong \GW_3^{[0]}(k) \oplus \GW_2^{[3]}(k),$
but since the group $\GW_2^{[3]}(k)$ is trivial by~\cite[Lemma~2.2]{FRS12}, the homomorphism $f'$ (and hence $f$) is surjective.
\end{proof}
